---
title: "Results"
author: "James Smith"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "docs") }) 
---

```{r setup, include=F}
rm(list = ls())

knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(devtools)
library(openair)
library(curl)
library(raster)
library(sp)
library(sf)
library(lubridate)
library(kableExtra)
library(rmarkdown)

## Coordinate reference information
latlong     = "+init=epsg:4326"
ukgrid      = "+init=epsg:27700"
google      = "+init=epsg:3857"

```

```{r get_monitoring_site_data, include=F}
# Get site locations that we scrape data for
site_results                <- read_csv('result.csv')

# Remove the manually added sitecode
site_results                <- site_results[substring(site_results$sitecode,1,2) != 'MA',]

# Remove where we weren't recording the actual datetime we used
site_results                <- site_results[!is.na(site_results$actual_datetime),]

# The scraped data is in BST so change to GMT
site_results$actual_datetime <- site_results$actual_datetime-3600
site_results$actual_datetime <- with_tz(site_results$actual_datetime, "GMT")

# Sites to import
sites_to_import             <- unique(site_results$sitecode)

# Get data from monitoring sites for the sites we sampled breezometer
monitoring_sites            <- importKCL(site = sites_to_import[1:130], year = 2018, units = 'volume')
monitoring_sites$site       <- NULL

site_results$join_time      <- as.POSIXct(format(site_results$actual_datetime, format = '%Y-%m-%d %H:00:00'), format = '%Y-%m-%d %H:%M:%S')
site_results$actual_datetime <- NULL
site_results$datetime       <- NULL
site_results                <- data.frame(site_results)

names(site_results)         <- paste0(names(site_results), '_model')
names(monitoring_sites)     <- paste0(names(monitoring_sites), '_monitor')

merged_data                 <- merge(site_results, monitoring_sites, by.x = c('join_time_model', 'sitecode_model'), by.y = c('date_monitor', 'code_monitor'))

names(merged_data)[1]       <- 'date'

site_type                   <- openair::importMeta(source = 'kcl')
site_type                   <- site_type[,c('code', 'site.type')]

merged_data                 <- merge(merged_data, site_type, by.x = c('sitecode_model'), by.y = c('code'))
```

# Comparisons at monitoring sites

## NO2

```{r no2, echo=F, message=FALSE, warning=FALSE, fig.width=12, fig.height=8}
timeVariation(merged_data, pollutant = c('no2_monitor', 'no2_model'), name.pol = c('Monitored (ug/m3)','External Model (ug/m3)'))
```

For NO2, we compare **`r length(unique(merged_data[!is.na(merged_data$no2_model) & !is.na(merged_data$no2_monitor),'sitecode_model']))`** sites hourly concentrations between `r min(merged_data[!is.na(merged_data$no2_model) & !is.na(merged_data$no2_monitor),'date'])` and `r max(merged_data[!is.na(merged_data$no2_model) & !is.na(merged_data$no2_monitor),'date'])`

```{r no2_stats, echo=F}
kable(modStats(mydata = merged_data, mod = 'no2_model', obs = 'no2_monitor', type = 'site.type')) %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```

## PM25

For PM2.5, we compare **`r length(unique(merged_data[!is.na(merged_data$pm25_model) & !is.na(merged_data$pm25_monitor),'sitecode_model']))`** sites hourly concentrations between `r min(merged_data[!is.na(merged_data$pm25_model) & !is.na(merged_data$pm25_monitor),'date'])` and `r max(merged_data[!is.na(merged_data$pm25_model) & !is.na(merged_data$pm25_monitor),'date'])`

```{r pm25, echo=F, results='hide', message=FALSE, warning=FALSE, fig.width=12, fig.height=8}
timeVariation(merged_data, pollutant = c('pm25_monitor', 'pm25_model'), name.pol = c('Monitored (ug/m3)','External Model (ug/m3)'))
```

```{r pm25_stats, echo=F}
kable(modStats(mydata = merged_data, mod = 'pm25_model', obs = 'pm25_monitor', type = 'site.type')) %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```

## PM10

For PM10, we compare **`r length(unique(merged_data[!is.na(merged_data$pm10_model) & !is.na(merged_data$pm10_monitor),'sitecode_model']))`** sites hourly concentrations between `r min(merged_data[!is.na(merged_data$pm10_model) & !is.na(merged_data$pm10_monitor),'date'])` and `r max(merged_data[!is.na(merged_data$pm10_model) & !is.na(merged_data$pm10_monitor),'date'])`

```{r pm10, echo=F, results='hide', message=FALSE, warning=FALSE, fig.width=12, fig.height=8}
timeVariation(merged_data, pollutant = c('pm10_monitor', 'pm10_model'), name.pol = c('Monitored (ug/m3)','External Model (ug/m3)'))
```

```{r pm10_stats, echo=F}
kable(modStats(mydata = merged_data, mod = 'pm10_model', obs = 'pm10_monitor', type = 'site.type')) %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```

## SO2

For SO2, we compare **`r length(unique(merged_data[!is.na(merged_data$so2_model) & !is.na(merged_data$so2_monitor),'sitecode_model']))`** sites hourly concentrations between `r min(merged_data[!is.na(merged_data$so2_model) & !is.na(merged_data$so2_monitor),'date'])` and `r max(merged_data[!is.na(merged_data$so2_model) & !is.na(merged_data$so2_monitor),'date'])`

```{r so2, echo=F, results='hide', message=FALSE, warning=FALSE, fig.width=12, fig.height=8}
timeVariation(merged_data, pollutant = c('so2_monitor', 'so2_model'), name.pol = c('Monitored (ug/m3)','External Model (ug/m3)'))
```

```{r so2_stats, echo=F}
kable(modStats(mydata = merged_data, mod = 'so2_model', obs = 'so2_monitor', type = 'site.type')) %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```

# Road transect comparison

```{r get_monitoring_site_data_again, include=F}
# Get site locations that we scrape data for
site_results          <- read_csv('result.csv')

# Remove the manually added sitecode
site_results          <- site_results[substring(site_results$sitecode,1,6) == 'MAN10_',]

plot_order            <- c('MAN10_5s', 'MAN10_4s', 'MAN10_3s', 'MAN10_2s', 'MAN10_1s', 'MAN10_1n', 'MAN10_2n', 'MAN10_3n', 'MAN10_4n', 'MAN10_5n')

site_results$sitecode <- factor(site_results$sitecode, levels = plot_order)

site_results          <- st_as_sf(site_results, coords = c("lon", "lat"), crs = 4326) %>% st_transform(27700)
```

```{r get_laei_data, include=F}
## Download the LAEI 2013 concentration files and unzip them we'll need
#concentrations_url    <- 'https://files.datapress.com/london/dataset/london-atmospheric-emissions-inventory-2013/2017-01-26T18:50:00/4.1.%20Concentrations%20LAEI%202013%20Update.zip'
#temp = tempfile()
#download.file(concentrations_url, temp)
#unzip(temp, exdir = ".")

setwd('Z:/James/Mini Projects/air_quality_modelling_agreement')

no2_2013                      <- raster('4.1. Concentrations LAEI 2013 Update/2013/ASCII/PostLAEI2013_2013_NO2.asc')
proj4string(no2_2013)         <- CRS(ukgrid)
site_results$kcl_no2          <- extract(no2_2013, site_results)
rm(no2_2013)

pm25_2013                     <- raster('4.1. Concentrations LAEI 2013 Update/2013/ASCII/PostLAEI2013_2013_PM25.asc')
proj4string(pm25_2013)        <- CRS(ukgrid)
site_results$kcl_pm25         <- extract(pm25_2013, site_results)
rm(pm25_2013)

pm10_2013                     <- raster('4.1. Concentrations LAEI 2013 Update/2013/ASCII/PostLAEI2013_2013_PM10.asc')
proj4string(pm10_2013)        <- CRS(ukgrid)
site_results$kcl_pm10         <- extract(pm10_2013, site_results)
rm(pm10_2013)

site_results                  <- st_transform(site_results, 4326)
```

## PM25

```{r pm25_road, echo=F, results='hide', message=FALSE, warning=FALSE, fig.width=12, fig.height=8}

ggplot(data=site_results, aes(st_coordinates(site_results)[,2], pm25)) + 
    annotate("rect", xmin = 51.548263, xmax = 51.548522, ymin = 8, ymax = 16,
        alpha = .6) +
  geom_smooth(aes(colour='External model')) +
  geom_smooth(data = site_results, aes(st_coordinates(site_results)[,2], kcl_pm25, colour='KCL Model')) +
  theme_bw() +
  theme(axis.ticks.x = element_blank(),
        axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        legend.title = element_blank(),
        axis.text.y = element_text(size=12),
        axis.title.y = element_text(size=14),
        legend.text = element_text(size=14))

```

## NO2

```{r no2_road, echo=F, results='hide', message=FALSE, warning=FALSE, fig.width=12, fig.height=8}

ggplot(data=site_results, aes(st_coordinates(site_results)[,2], no2)) + 
    annotate("rect", xmin = 51.548263, xmax = 51.548522, ymin = 15, ymax = 40,
        alpha = .6) +
  geom_smooth(aes(colour='External model')) +
  geom_smooth(data = site_results, aes(st_coordinates(site_results)[,2], kcl_no2, colour='KCL Model')) +
  theme_bw() +
  theme(axis.ticks.x = element_blank(),
        axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        legend.title = element_blank(),
        axis.text.y = element_text(size=12),
        axis.title.y = element_text(size=14),
        legend.text = element_text(size=14))

```

## PM10

```{r pm10_road, echo=F, results='hide', message=FALSE, warning=FALSE, fig.width=12, fig.height=8}

ggplot(data=site_results, aes(st_coordinates(site_results)[,2], pm10)) + 
    annotate("rect", xmin = 51.548263, xmax = 51.548522, ymin = 15, ymax = 26,
        alpha = .6) +
  geom_smooth(aes(colour='External model')) +
  geom_smooth(data = site_results, aes(st_coordinates(site_results)[,2], kcl_pm10, colour='KCL Model')) +
  theme_bw() +
  theme(axis.ticks.x = element_blank(),
        axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        legend.title = element_blank(),
        axis.text.y = element_text(size=12),
        axis.title.y = element_text(size=14),
        legend.text = element_text(size=14))

```